\documentclass[letter,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{ebgaramond}
\usepackage{textcomp}
\geometry{left=.75in, right=.75in, top=.75in, bottom=.75in}

\begin{document}

%======================
%   Header
%======================
\begin{center}
    {\Huge \textbf{Douglas Ronne}}\\
    \vspace{2mm}
    1068 Fir St SE| Olympia, WA, 98501\\
    \href{mailto:vextorspace@gmail.com}{vextorspace@gmail.com} | (360) 797-2009\\
    \href{www.linkedin.com/in/douglas-ronne-7133272a}{linkedin.com/in/douglas-ronne-7133272a} | \href{https://github.com/vextorspace}{github.com/vextorspace}
\end{center}

Dear Hiring Manager,

I am excited to apply for a position with Cruise. I have been working in software development most of my life, but I have also been working on software that has a real effect on the world, whether it is embedded software or CAD software or a custom ERP system. I appreciate when I can affect the world for the better. Building the tools for the engineers to do their jobs is also a very important task. 

I did a lot of customer outreach where I would try to learn what their real problems were and how I could solve them. I have always been very empathetic to others' issues and find it easy to relate to them. It is easier to do this when you actually work with the people you are working for every day.

Thank you for considering me for your role.
\\
Sincerely,\\
--Douglas Ronne
\end{document}
