\documentclass[letter,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{ebgaramond}
\usepackage{textcomp}
\geometry{left=.75in, right=.75in, top=.75in, bottom=.75in}

\begin{document}

%======================
%   Header
%======================
\begin{center}
    {\Huge \textbf{Douglas Ronne}}\\
    \vspace{2mm}
    1068 Fir St SE| Olympia, WA, 98501\\
    \href{mailto:vextorspace@gmail.com}{vextorspace@gmail.com} | (360) 797-2009\\
    \href{www.linkedin.com/in/douglas-ronne-7133272a}{linkedin.com/in/douglas-ronne-7133272a} | \href{https://github.com/vextorspace}{github.com/vextorspace}
\end{center}

Dear Hiring Manager,
I am excited to apply for a position with Equal Experts. I love working on different problems all the time. I know many different languages, have experience in embedded software, signal processing, data analysis, management, and drafting to name a few. I would love to do consulting work as it would allow me to continue learning every day. My math background makes Scala a lovely language. I am very good at seeing what makes a problem special and finding novel solutions. At my last job I helped us define common sense so we could try to teach it to our new engineers: The knowledge and experience to understand what the effects of a decision or action might be, combined with the habit of pausing before acting to think for a minute.


Finally, I did a lot of customer outreach where I would try to learn what their real problems were and how I could solve them. I have always been very empathetic to others' issues and find it easy to relate.

Thank you for considering me for your role.
\\
Sincerely,
--Douglas Ronne
\end{document}
