\documentclass[letter,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{ebgaramond}
\usepackage{textcomp}
\geometry{left=.75in, right=.75in, top=.75in, bottom=.75in}

\begin{document}

%======================
%   Header
%======================
\begin{center}
    {\Huge \textbf{Douglas Ronne}}\\
    \vspace{2mm}
    1068 Fir St SE| Olympia, WA, 98501\\
    \href{mailto:vextorspace@gmail.com}{vextorspace@gmail.com} | (360) 797-2009\\
    \href{www.linkedin.com/in/douglas-ronne-7133272a}{linkedin.com/in/douglas-ronne-7133272a} | \href{https://github.com/vextorspace}{github.com/vextorspace}
\end{center}

Dear Hiring Manager,

I am excited to apply for a position with the Allen Brain Institute. I have worked as a professional software developer for about 25 years, and was an amateur since I was 8 years old. I heard about the Allen Brain institute when I worked with Protocase as our sister company 45 Drives did work with you. The team that went out there included Rob MacQueen whom I mentored for several years. He spoke very highly of your company and its mission.

I have always enjoyed my roles that included hardware integration and scientific exploration and research the most. I enjoy coding in many languages, including C,C++,C\#, Python, Java, Jotlin, Matlab, and Rust. I also love collaborating with non-engineering teams in development, deployment, and testing of the software products I help create. There is nothing as satisfying as solving the real problem a customer or colleague has!

I have also acquired a love of good project management and working with cross-functional teams to do software architecture and hardware/ software integration on complex products.

Thank you for considering me for your role.
\\
Sincerely,\\
--Douglas Ronne
\end{document}
