\documentclass[letter,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{ebgaramond}
\usepackage{textcomp}
\usepackage{titlesec}

\geometry{left=.75in, right=.75in, top=.75in, bottom=.75in}


\titleformat{\section}
    {\normalfont\Large\bfseries}
    {}{0pt}
    {\titlerule[1pt]\MakeUppercase}
    [\titlerule]
    
    
\newenvironment{noindentblock}{%
  \begin{list}{}{%
    \setlength{\leftmargin}{0in} % Set the indent width
    \setlength{\rightmargin}{.25in} % Set the right margin (optional)
    \setlength{\topsep}{0pt} % Remove additional vertical space
    \setlength{\parsep}{0pt} % Remove additional vertical space
  }
  \item[]}{\end{list}}


\begin{document}

%======================
%   Header
%======================
\begin{center}
    {\Huge \textbf{Douglas Ronne}}\\
    \vspace{2mm}
    1068 Fir St SE | Olympia, WA, 98501\\
    \href{mailto:vextorspace@gmail.com}{vextorspace@gmail.com} | (360) 797-2009\\
    \href{https://www.linkedin.com/in/vextorspace}{linkedin.com/in/vextorspace} | \href{https://github.com/vextorspace}{github.com/vextorspace} | \href{https://ronnev.substack.com}{ronnev.substack.com}
\end{center}

%======================
%   Introduction
%======================
\section*{Introduction}

I am collaborative, driven by the success of my team, take responsibility, have an adaptive and flexible approach to problem solving, and am now seeking a new challenge to apply my technical and leadership skills. In addition to being very technically capable I am a skilled communicator and easy to get along with. I am driven to solve problems for the people around me whether my colleagues or customers. I am a citizen of the U.S.A. and Canada.

%======================
%   Skills
%======================
\section*{Skills}
\begin{itemize}[leftmargin=*,itemsep=0pt, parsep=0pt,label=$\diamond$]
\item \textbf{Languages:} Assembly, Visual Basic, C/C++/C\#, Groovy, Java, Kotlin, LaTeX, Matlab, Python, Rust, Scala
\item \textbf{Programming:} Agile Methods, Test Driven Development, Behavior Driven Development, Automated Testing, Refactoring, Design Patterns, Legacy Code Techniques, GitHub, GitLab, Continuous Integration, Continuous Delivery, Jenkins, gitlab-ci, CodeScene, Threading, Microservices, IntelliJ, Netbeans, Emacs, Linux, Windows, VMWare, 3D Modeling, Data Analysis, System Analysis, Risk Assessment, Debugging, GDB, Linkers, Makefiles, Code Review, Scripting, Bash, Distributed Systems, DevOps, Customer Feedback
\item \textbf{Management:} Mentoring, Conflict Resolution, Estimation, Training, Critical Path Analysis, Problem Solving, Scrum, Kanban, Project Management, Failure Analysis, Hiring, Performance Reviews
\end{itemize}

%======================
%   Experience
%======================
\section*{Experience}
\noindent
\textbf{R\&D Manager - Protocase Inc}, Sydney, NS, CANADA \hfill \textit{September 2009 - January 2024}
\begin{itemize}[leftmargin=*,itemsep=0pt, parsep=0pt,label=$\diamond$]
\item As the sole developer I created from scratch our flagship sheet metal enclosure CAD software on schedule. This software brings in about \$5mil in revenue and about 20\% of new customers.
\item I grew the software team from 1 person to 10 people allowing us to expand our reach and not just maintain/ grow our CAD software but also create custom ERP software and much more.
\item I took over the mechanical and industrial engineering teams and expanded the team from myself as the sole contributer to a high-performing team of about 25 professionals.
\item Created custom formula parser language for dynamic parsing of variables and sub formulas in template CAD models. 
\item Visited customers to help them use our tools and better understand what they needed from us.
\item Developed internal Automated Work Instructions on top of CAD to go from customer design to shop build sheets reducing rework by as much as 30\% at some processes.
\item Actively contributed to executive management, providing strategic direction and problem solving, helping to grow the company from 40 people and \$1mil in revenue to 400 people and over \$50mil in revenue.
\item Created vision software to optimize print bed part location. Reduced rework rate by 50\% and doubled productivity.
\end{itemize}

\noindent
\textbf{Head of Software - Power Control Engineering}, Grants Pass, OR\hfill \textit{May 2005 - May 2009}
\begin{itemize}[leftmargin=*,itemsep=0pt, parsep=0pt,label=$\diamond$]
\item As the sole developer I created embedded software for a Separately Excited Motor Controller for high-powered golf carts.
\item Created a custom build and debug system in Python that shortened deploy time by about 50\%.
\item Discovered and reported a bug in the Texas Instruments C Compiler involving large switch statements.
\end{itemize}

\pagebreak
\noindent
\textbf{Senior Multidisciplined Engineer 3 - Raytheon}, El Segundo, CA\hfill \textit{August 2001 - May 2005}
\begin{itemize}[leftmargin=*,itemsep=0pt, parsep=0pt,label=$\diamond$]
\item Designed algorithms for anti-jam GPS and radar systems, as well as conducted lab testing.
\item Delivered 3 projects on time and under budget as the team lead of programmers and analyst.
\item Utilized Matlab, C, C++, Ada, VHDL, and microcode on FPGAs for large matrix inversion.
\item Demonstrated solutions and updates live to customers.
\end{itemize}

\noindent
\textbf{Math Teacher - Western Washington University}, Bellingham, WA\hfill \textit{August 1997 - June 2001}
\begin{itemize}[leftmargin=*,itemsep=0pt, parsep=0pt,label=$\diamond$]
\item Taught algebra, precalculus, and business calculus classes.
\item Operated a math tutoring lab and tutored everything from algebra to multivariate calculus.
\end{itemize}

%======================
%   Bookshelf
%======================
\section*{Most Influential Books in My  Bookshelf}
``Test Driven Development'', ``Growing Object Oriented Software, Guided By Tests'', ``Refactoring'', ``Refactoring to Patterns'', ``Working Effectively with Legacy Code'', ``Your Code as a Crime Scene'', ``Tidy First'', ``Clean Code'', ``Crucial Conversations'', ``Getting Things Done - The Art of Stress-free Productivity'', ``Extreme Ownership''

%======================
%   Education
%======================
\section*{Education}

\noindent
\textbf{Western Washington University}, Bellingham, WA \hfill \textit{2001}\\
\textit{Mathematics, MS - 4.0 GPA} 
\begin{noindentblock}
Courses in numerical computing, windows programming, theoretical and applied math.
\end{noindentblock}

\noindent
\textbf{Western Washington University}, Bellingham, WA \hfill \textit{1999}\\
\textit{Mathematics, BS - 3.96 GPA}
\begin{noindentblock}
Courses in numerical computing, data structures, assembly language.
\end{noindentblock}

\noindent
\textbf{South Puget Sound Community College}, Olympia, WA \hfill \textit{1996}\\
\textit{General Studies, Associate of Arts - 3.92 GPA}
\begin{noindentblock}
Courses in math, computer science, english, physical and social sciences.
\end{noindentblock}

\noindent
\textbf{South Puget Sound Community College}, Olympia, WA \hfill \textit{June 1993}\\
\textit{Electronics, Associate of Technical Arts - 3.88 GPA}
\begin{noindentblock}
Courses in theory and practical electronics, machine language, assembly programming, and troubleshooting.
\end{noindentblock}

%======================
%   Professional Development
%======================
\section*{Professional Development}
\noindent
\textbf{Front end web development in Rust}, Udemy \hfill \textit{2024}

\noindent
\textbf{RustConf 2024} \hfill \textit{2024}

\noindent
\textbf{Build a RC5 Symmetric Block Cipher in Rust}, Udemy \hfill \textit{2024}

\noindent
\textbf{Ultimate Rust Crash Course}, Udemy \hfill \textit{2024}

\noindent
\textbf{Ultimate Rust 2: Intermediate Concepts} Udemy, \hfill \textit{2024}

\noindent
\textbf{Learn Rust by Building Real Applications} Udemy, \hfill \textit{2024}

\noindent
\textbf{The World's Best Intro to TDD}, jbrains.ca \hfill \textit{2024}

\noindent
\textbf{Level 1 Fire Training}, Nova Scotia Fire School \hfill \textit{2020}

\noindent
\textbf{Protocase Conflict Management}, Protocase \hfill \textit{2018}

\noindent
\textbf{SolidWorks API Training}, SolidWorks \hfill \textit{2014}

\noindent
\textbf{Power Control Engineering Workshop}, University of Wisconsin \hfill \textit{2007}

\noindent
\textbf{Raytheon Six Sigma}, Raytheon \hfill \textit{2003}

\noindent
\textbf{Raytheon Systems Engineering}, Raytheon \hfill \textit{2004}

\noindent
\textbf{Multirate Signal Processing}, fred harris \hfill \textit{2002}

\pagebreak
%======================
%   Volunteering
%======================
\section*{Volunteering}
\noindent
\textbf{Lieutenant, Baddeck Volunteer Fire Department}, Baddeck, NS, CANADA\hfill \textit{September 2012 - June 2022}
\begin{noindentblock}
  I started as a rank and file firefighter and became the lieutenant on our rescue truck and the Treasurer. Also took level 1 firefighter training.
\end{noindentblock}

\noindent
\textbf{Generalist, Pan Cape Breton Food Hub}, Baddeck, NS, CANADA\hfill \textit{September 2014 - June 2022}
\begin{noindentblock}
  I helped the executive director design processes and assisted with general operations, maintenance, and labor.
\end{noindentblock}

\noindent
\textbf{Volunteer and Board Chair, Baddeck Farmers Market}, Baddeck, NS, CANADA\hfill \textit{March 2009 - June 2014}
\begin{noindentblock}
  I helped the executive director design processes and assisted with general operations, maintenance, and labor. I was the board chair for 2 years.
\end{noindentblock}

\section*{Interests}
\begin{itemize}
\item Sailing
\item Cooking
\item Hiking
\item Snowboarding
\item Programming
\item Travelling
\item Reading
\item Programming for fun
\item Embedded software
\item Experimenting with productivity tools
\end{itemize}
\end{document}

